### 2023-04-06 reachable-resilience.tex
details
up

\problemx{Downward-reachability problem}
{A transition system $\mathscr{S}=(S,\rightarrow)$, $s \in S$ and a downward-closed set $D
\subseteq S$.}
{$\exists s' \in D ~ s \to^* s'$? \newline}

@@

\begin{proposition}
Let $V= (Q,T)$ be a $d$-VASS and $v \in \N^d$ a configuration, then one can compute a basis of $\uparrow \post^*(v)$.
\end{proposition}
%\alain{mauvaises notations, la tradition est que P est l'ensemble des places...les états/markings en minuscules,....}

>>>>

\problemx{Downward-reachability problem}
{A transition system $\mathscr{S}=(S,\rightarrow)$, $s \in S$ and a downward-closed set $D
\subseteq S$.}
% {$\exists s' \in D ~ s \to^* s'$? \newline}\alain{ecrire $s  \to^* D$}
{$s  \to^* D$? \newline}

@@

\begin{proposition}
Let $V= (Q,T)$ be a $d$-VASS and $q(\textbf{v}) \in Q \times \N^d$ a configuration, then one can compute a basis of $\uparrow \post^*(q(\textbf{v}))$.
\end{proposition}
%\alain{mauvaises notations, la tradition est que P est l'ensemble des places...les états/markings en minuscules,....}
